Complementary Filters Shaping Using $\mathcal{H}_\infty$ Synthesis

### 2019-10-30 poster/conclusion.tex
Update poster
Poster: Worked on the ligo part

This paper has shown how complementary filters can be used to combine multiple sensors in order to obtain a super sensor.
Typical specification on the super sensor noise and on the robustness of the sensor fusion has been shown to be linked to the norm of the complementary filters.
Therefore, a synthesis method that permits the shaping of the complementary filters norms has been proposed and has been successfully applied for the design of complex filters.
Future work will aim at further developing this synthesis method for the robust and optimal synthesis of complementary filters used in sensor fusion.

>>>>

%%% Local Variables:
%%% TeX-master: "poster"
%%% End:

Complementary filters can be used to \textbf{combine multiple sensors} in order
to obtain a \textbf{super sensor}.
Specification on the \textbf{super sensor noise} and on the \textbf{robustness
  of the sensor fusion} are linked to the \textbf{norm of the complementary filters}.
A synthesis method that permits the \textbf{shaping of the complementary filters
  norms} has been proposed and has been successfully applied for the design of
complex filters.

### 2019-10-30 poster/ligo.tex
Poster: Worked on the ligo part

The specifications for one pair of complementary filters used at the LIGO are
detailed in \cite{hua04_polyp_fir_compl_filter_contr_system} and shown in the
frequency domain in Fig.~\ref{fig:ligo_weights}.

\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Specifications and weighting functions magnitude used for $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.49\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters (solid) designed in \cite{hua05_low_ligo} with the filters obtained with $\mathcal{H}_\infty$ synthesis (dashed)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}

>>>>

The effectiveness of the proposed method is demonstrated by designing a
complementary filter pair that is used in the active isolation system at the LIGO
\cite{hua05_low_ligo}.
The requirements are very tight (shown by dashed upper bounds
in Fig.~\ref{fig:ligo_weights}) and thus their design is complex.

\bigskip

\begin{minipage}[t]{0.48\linewidth}
  The weights are designed such that their inverse magnitude is as
  close as possible to the specifications while being of reasonably \textbf{small order}
  (Fig.~\ref{fig:ligo_weights}).
  After synthesis, the obtained complementary filters are
  compared with the FIR filters \cite{hua05_low_ligo} and are found
  to be very close to each other (Fig.~\ref{fig:comp_fir_ligo_hinf}).
  \begin{tikzfigure}[Specifications and weights used for the $\mathcal{H}_\infty$ synthesis]
    \label{fig:ligo_weights}
    \centering
    \includegraphics[width=\linewidth]{figs/ligo_weights.pdf}
  \end{tikzfigure}
\end{minipage}\hfill
\begin{minipage}[t]{0.5\linewidth}
  \begin{tikzfigure}[Comparison of the FIR filters designed
    in \cite{hua05_low_ligo} (order 512) with the filters obtained with $\mathcal{H}_\infty$
    synthesis (order 28)]
    \label{fig:comp_fir_ligo_hinf}
    \centering
    \includegraphics[width=\linewidth]{figs/comp_fir_ligo_hinf.pdf}
  \end{tikzfigure}
\end{minipage}
